### 2024-04-08 README.qmd
Small fixes

@@

```{r}
table(d$OFFENCE) |>
  sort()
```

```{r}
d |>
  # Reduce nchar of OFFENCE
  mutate(OFFENCE = stringr::str_sub(OFFENCE, 1, 60)) |>
  group_by(OFFENCE) |>
  # Count number of rows in each group
  mutate(n = n()) |>
  filter(n > nrow(d) / 50)|>
  ggplot() +
  geom_bar(aes(OFFENCE)) +
  # Make x labels vertical
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

>>>>

The data looks like this (first 3 rows shown):

```{r}
d |>
  head(3) |>
  knitr::kable()
```

@@

```{r}
table(d$offence) |>
  sort()
```

```{r}
d |>
  # Reduce nchar of offence
  mutate(offence = stringr::str_sub(offence, 1, 60)) |>
  group_by(offence) |>
  # Count number of rows in each group
  mutate(n = n()) |>
  filter(n > nrow(d) / 50)|>
  ggplot() +
  geom_bar(aes(offence)) +
  # Make x labels vertical
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
